---
output: 
# learnr::tutorial
html_document:
    toc: true
    toc_depth: 2
    toc_float: true
    fig_width: 7
    fig_height: 6
    fig_caption: true
    theme: lumen
    df_print: paged
    code_folding: show
runtime: shiny_prerendered
title: "How do you compare against these historic NY Marathon first place winners?"
subtitle: "SDS 192 Mini Project 1"
author: "Victoria Devlin McLoughlin, Katelyn Diaz, Margot Draillard-Vandenberg"
date: "`r format(Sys.Date(), '%B %e, %Y')`"

---
---

```{r setup, include=FALSE, message = FALSE}
# install.packages("learnr")
library(learnr)
library(tidyverse)
library(openintro)
library(sds192)

knitr::opts_chunk$set(echo = FALSE)
```



```{r load data (DATA PREP), message=FALSE, include = FALSE}
marathon
# {r sort data}
marathon<-marathon%>%
  arrange(year)
```

## Section 1: Plot
```{r plotting, message=FALSE}
marplot<-ggplot(data = marathon, aes(x = year, y = time, color= time))+
  geom_point()+
  geom_line()+
  facet_wrap(~gender)+
  labs(title="NY City Marathon Times from 1970 to 1999",
       subtitle="Sourced from New York Road Runners Club",
       x= "Race Year",
       y ="First Place Run Time (Hours) ")+
  scale_color_continuous(breaks = c(2.134,2.391,3.1447),
                         labels = c(2.134, 2.391, 3.145),
                         low = "red", high = "blue")
marplot
```

## Section 3: Test your knowledge!

##### Test your knowledge of running and how well you know you would fare against some of these first place marathon runners! 


```{r Questions}
quiz(
  question("What is the average speed of female marathon runners?",
    answer("8.68 minutes/mile"),
    answer("15 minutes/mile"),
    answer("11.55 minutes/mile", correct = TRUE),
    answer("10.34 miles/min")
  ),
  question("What is the average speed of male marathon runners?",
    answer("8.68 minutes/mile"),
    answer("15 minutes/mile"),
    answer("11.55 minutes/mile"),
    answer("10.34 miles/min", correct = TRUE)
  ),
  question("How many miles are there in a marathon?",
    answer("26.2 kilometers"),
    answer("13.1 miles"),
    answer("26.2 miles", correct = TRUE),
    answer("5 kilometers")
  ),
  question("Why is there not a female winner in 1970?",
    answer("Only one female entered and she was unable to finish due to injury", correct = TRUE),
    answer("No females were allowed to enter"),
    answer("The female that entered registered as male"),
    answer("All of the females that entered dropped out")
  )
)
```
## Section 4: Sources:
 - https://rstudio.github.io/learnr/
 - https://www.runnersworld.com/uk/training/marathon/a27787958/average-marathon-finish-time/#:~:text=What%20is%20the%20average%20pace,or%20an%2011.55%20minute%20mile.
 - 
 



## Word count

```{r word_count, message=FALSE, echo=FALSE}
text_stats()
```

## Standards

In this assignment, we attempted the following [standards](https://beanumber.github.io/sds192/standards.html):

- `r standard_button("markdown")`: We met the Markdown standard because we...
- `r standard_button("aesthetics")`: We met the Aesthetics standard because we...


